Evaluate PEER in each cohort and brain region

### 2021-02-17 combined_analysis/eval_resid_in_each.Rmd
add CTS
add more summary info

METADATA %>% group_by(Dx, Institution, Reported_Gender, Region) %>% dplyr::summarise(count = n()) %>% 
kable(caption="Diagnosis, Institution, Sex, Region") %>% kable_styling(full_width=FALSE) 
```

@@

@@

    PEER_setPhenoMean(model, t(geneExpr[1:100,i,]))

@@

    PEER_setNk(model,2)

@@

    # upload latent variables
    file = paste0('PEER',gsub(" ", '', gsub("-", "_", datID)), '_', CT, ".RDS")
    storeData( latentVariables, file, paste0(datID, " Latent variables for QTL analysis", ' - ', CT))
  }
}
```

>>>>

METADATA %>% group_by(Dx, Institution, Reported_Gender, Region) %>% dplyr::summarise(count = n()) %>% kable(caption="Diagnosis, Institution, Sex, Region") %>% kable_styling(full_width=FALSE)

METADATA %>% group_by(Ethnicity, Institution, Region) %>% dplyr::summarise(count = n()) %>% kable(caption="Ethnicity, Institution, Region") %>% kable_styling(full_width=FALSE)

METADATA %>% group_by(Ethnicity, Cohort, Region) %>% dplyr::summarise(count = n()) %>%  kable(caption="Ethnicity, Cohort, Region") %>% kable_styling(full_width=FALSE) 
```

@@

  nEXP_OBJ = File(file, 
                  name = description, 
                  parentId = CODE$properties$id)
  # synStore(nEXP_OBJ, used = ALL_USED_IDs, executed = thisFile)
}
```

@@

    PEER_setPhenoMean(model, t(geneExpr[,i,]))

@@

@@

    # upload latent variables
    file = paste0('PEER_',gsub(" ", '', gsub("-", "_", datID)), '_', CT, ".RDS")
    storeData( latentVariables, file, paste0(datID, " Latent variables for QTL analysis", ' - ', CT))
  }
}
```

for FILE in $(ls PEER*)
do
  mv $FILE $(echo $FILE | sed 's/PEER/PEER_/')
done
